% TEX encoding=UTF-8 Unicode
\documentclass{article}

%\include{head}
\usepackage[official]{eurosym}

\begin{document}

%\input{head}
\section{The Structure of Text and Language}
\ldots when Einstein introduced his formula
\begin{equation}
  e = m \cdot c^2 \; ,
\end{equation}
% 换行 
which is at the same time the most widely known \\
and the least well understood physical formula. \\
``kkkk''\\
\today 
% 
\euro\\
Not shelfful\
but shelf\mbox{}ful
ffffff

%% \chapter[Title for the table of contents]{
%%   A long
%%   and especially boring title, shown in the text}

%
Footnotes\footnote{This is
  a footnote.} are often used
by people using \LaTeX.

\underline{this is underline.}

\emph{If you use
  emphasizing inside a piece
  of emphasized text, then
  \LaTeX{} uses the
  \emph{normal} font for
  emphasizing.}

\textit{You can also
  \emph{emphasize} text if
  it is set in italics,}
\textsf{in a
  \emph{sans-serif} font,}
\texttt{or in
\emph{typewriter} style.}

\begin{flushleft}
  This text is\\ left-aligned.
  \LaTeX{} is not trying to make
  each line the same length.
\end{flushleft}

\begin{flushright}
  This text is\\ right-aligned.
  \LaTeX{} is not trying to make
  each line the same length.
\end{flushright}

\begin{center}
  This text is\\ center.
\end{center}

A typographical rule of thumb
for the line length is:
\begin{quote}
  On average, no line should
  be longer than 66 characters.
\end{quote}
This is why \LaTeX{} pages have
such large borders by default
and also why multicolumn print
is used in newspapers.

I know only one English poem by
heart. It is about Humpty Dumpty.
\begin{flushleft}
  \begin{verse}
    Humpty Dumpty sat on a wall:\\
    Humpty Dumpty had a great fall.\\
    All the King’s horses and all
    the King’s men\\
    Couldn’t put Humpty together
    again.
  \end{verse}
\end{flushleft}


\begin{abstract}
  The abstract abstract.
\end{abstract}

The \verb|\ldots| command \ldots
\begin{verbatim}
10 PRINT ``HELLO WORLD ''
20 GOTO 10
\end{verbatim}

\begin{verbatim*}
the starred version of
the          verbatim
environment emphasizes
the spaces  in the text
\end{verbatim*}

\newpage
EQUATION
\newpage
EQUATION

\end{document}
